Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-28 paper/paper.qmd
added mil spending graph

>>>>

df_filtered <- df %>%
  filter(format(award_date, "%Y") != "2019")

df_filtered$year <- format(df_filtered$award_date, "%Y")

# Filter for military spending (where buyer is "National Defence")
public_services_df <- df_filtered %>%
  filter(buyer == "Public Services and Procurement Canada")

# Summarize total spending per year
public_spending_per_year <- public_services_df %>%
  group_by(year) %>%
  summarize(total_spending = sum(amount, na.rm = TRUE))

# Create the bar chart
ggplot(data = public_spending_per_year, aes(x = year, y = total_spending)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Public Services Spending Per Year", x = "Year", y = "Total Spending") +
  theme_minimal() +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  theme(plot.title = element_text(hjust = 0.5))
